Report on Certificate Tools

### 2016-10-13 TEX/draft.tex
Added GnuTLS, some parts little bit rough

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???                                                                         \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5} 
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

@@

@@

@@

>>>>

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuPG                  &                                                                      &                             &                             &                             &                             &                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keytool                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
GnuPG                  &                               &                                          &                                                &                                            &                                                                             \\ \hline
Keystore explorer      & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
XCA                    & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & ???                                                                         \\ \hline
GnuTLS                 & \cellcolor[HTML]{34FF34}Yes   & ???	                                  & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{FE0000}No                                                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{Conversions}                                                                                                                                            \\ \cline{2-5} 
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-3}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FE0000}No  & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuPG                   &                                  &                             &                                         &                                                                  \\ \hline
Keystore explorer       & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes             & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
XCA                     & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
GnuTLS                  & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{FF3A3A}No  & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Self-signed certificate}
To generate a self-signed certificate it is needed to generate a a private key. Generating of key is done by following command:
\begin{verbatim}
 certtool --generate-privkey --outfile [file.pem] --[rsa|dsa|ecc] \
          --sec-param=[low|legacy|medium|high|ultra]
\end{verbatim}
Where \verb+sec-param=<length_alias>+ and will be discussed in next parts.

To create a self-signed certificate with created private key use:
\begin{verbatim}
certtool --generate-self-signed --load-privkey ca-key.pem \
         [--template cert.cfg] --hash=[look@algorithm_part] --outfile ca-cert.pem
\end{verbatim}

More options when generating self-signed certificate (or a CSR) you need to create a config file which has structure as follows (copied from a man page):
\begin{verbatim}
# X.509 Certificate options
#
# DN options

# The organization of the subject.
organization = "Koko inc."

# The organizational unit of the subject.
unit = "sleeping dept."

# The locality of the subject.
# locality =

# The state of the certificate owner.
state = "Attiki"

# The country of the subject. Two letter code.
country = GR

# The common name of the certificate owner.
cn = "Cindy Lauper"

# A user id of the certificate owner.
#uid = "clauper"

# Set domain components
#dc = "name"
#dc = "domain"

# If the supported DN OIDs are not adequate you can set
# any OID here.
# For example set the X.520 Title and the X.520 Pseudonym
# by using OID and string pairs.
#dn_oid = "2.5.4.12 Dr."
#dn_oid = "2.5.4.65 jackal"

# This is deprecated and should not be used in new
# certificates.
# pkcs9_email = "none@none.org"

# An alternative way to set the certificate's distinguished name directly
# is with the "dn" option. The attribute names allowed are:
# C (country), street, O (organization), OU (unit), title, CN (common name),
# L (locality), ST (state), placeOfBirth, gender, countryOfCitizenship, 
# countryOfResidence, serialNumber, telephoneNumber, surName, initials, 
# generationQualifier, givenName, pseudonym, dnQualifier, postalCode, name, 
# businessCategory, DC, UID, jurisdictionOfIncorporationLocalityName, 
# jurisdictionOfIncorporationStateOrProvinceName,
# jurisdictionOfIncorporationCountryName, XmppAddr, and numeric OIDs.

#dn = "cn = Nikos,st = New\, Something,C=GR,surName=Mavrogiannopoulos,2.5.4.9=Arkadias"

# The serial number of the certificate
# Comment the field for a time-based serial number.
serial = 007

# In how many days, counting from today, this certificate will expire.
# Use -1 if there is no expiration date.
expiration_days = 700

# Alternatively you may set concrete dates and time. The GNU date string 
# formats are accepted. See:
# http://www.gnu.org/software/tar/manual/html_node/Date-input-formats.html

#activation_date = "2004-02-29 16:21:42"
#expiration_date = "2025-02-29 16:24:41"

# X.509 v3 extensions

# A dnsname in case of a WWW server.
#dns_name = "www.none.org"
#dns_name = "www.morethanone.org"

# An othername defined by an OID and a hex encoded string
#other_name = "1.3.6.1.5.2.2 302ca00d1b0b56414e5245494e2e4f5247a11b3019a006020400000002a10f300d1b047269636b1b0561646d696e"
#other_name_utf8 = "1.2.4.5.6 A UTF8 string"
#other_name_octet = "1.2.4.5.6 A string that will be encoded as ASN.1 octet string"

# Allows writing an XmppAddr Identifier
#xmpp_name = juliet@im.example.com

# Names used in PKINIT
#krb5_principal = user@REALM.COM
#krb5_principal = HTTP/user@REALM.COM

# A subject alternative name URI
#uri = "http://www.example.com"

# An IP address in case of a server.
#ip_address = "192.168.1.1"

# An email in case of a person
email = "none@none.org"

# TLS feature (rfc7633) extension. That can is used to indicate mandatory TLS
# extension features to be provided by the server. In practice this is used
# to require the Status Request (extid: 5) extension from the server. That is,
# to require the server holding this certificate to provide a stapled OCSP response.
# You can have multiple lines for multiple TLS features.

# To ask for OCSP status request use:
#tls_feature = 5

# Challenge password used in certificate requests
challenge_password = 123456

# Password when encrypting a private key
#password = secret

# An URL that has CRLs (certificate revocation lists)
# available. Needed in CA certificates.
#crl_dist_points = "http://www.getcrl.crl/getcrl/"

# Whether this is a CA certificate or not
#ca

# Subject Unique ID (in hex)
#subject_unique_id = 00153224

# Issuer Unique ID (in hex)
#issuer_unique_id = 00153225

#### Key usage

# The following key usage flags are used by CAs and end certificates

# Whether this certificate will be used to sign data (needed
# in TLS DHE ciphersuites). This is the digitalSignature flag
# in RFC5280 terminology.
signing_key

# Whether this certificate will be used to encrypt data (needed
# in TLS RSA ciphersuites). Note that it is preferred to use different
# keys for encryption and signing. This is the keyEncipherment flag
# in RFC5280 terminology.
encryption_key

# Whether this key will be used to sign other certificates. The
# keyCertSign flag in RFC5280 terminology.
#cert_signing_key

# Whether this key will be used to sign CRLs. The
# cRLSign flag in RFC5280 terminology.
#crl_signing_key

# The keyAgreement flag of RFC5280. It's purpose is loosely
# defined. Not use it unless required by a protocol.
#key_agreement

# The dataEncipherment flag of RFC5280. It's purpose is loosely
# defined. Not use it unless required by a protocol.
#data_encipherment

# The nonRepudiation flag of RFC5280. It's purpose is loosely
# defined. Not use it unless required by a protocol.
#non_repudiation

#### Extended key usage (key purposes)

# The following extensions are used in an end certificate
# to clarify its purpose. Some CAs also use it to indicate
# the types of certificates they are purposed to sign.

# Whether this certificate will be used for a TLS client;
# this sets the id-kp-serverAuth (1.3.6.1.5.5.7.3.1) of 
# extended key usage.
#tls_www_client

# Whether this certificate will be used for a TLS server;
# This sets the id-kp-clientAuth (1.3.6.1.5.5.7.3.2) of 
# extended key usage.
#tls_www_server

# Whether this key will be used to sign code. This sets the
# id-kp-codeSigning (1.3.6.1.5.5.7.3.3) of extended key usage
# extension.
#code_signing_key

# Whether this key will be used to sign OCSP data. This sets the
# id-kp-OCSPSigning (1.3.6.1.5.5.7.3.9) of extended key usage extension.
#ocsp_signing_key

# Whether this key will be used for time stamping. This sets the
# id-kp-timeStamping (1.3.6.1.5.5.7.3.8) of extended key usage extension.
#time_stamping_key

# Whether this key will be used for email protection. This sets the
# id-kp-emailProtection (1.3.6.1.5.5.7.3.4) of extended key usage extension.
#email_protection_key

# Whether this key will be used for IPsec IKE operations (1.3.6.1.5.5.7.3.17).
#ipsec_ike_key

## adding custom key purpose OIDs

# for microsoft smart card logon
# key_purpose_oid = 1.3.6.1.4.1.311.20.2.2

# for email protection
# key_purpose_oid = 1.3.6.1.5.5.7.3.4

# for any purpose (must not be used in intermediate CA certificates)
# key_purpose_oid = 2.5.29.37.0

### end of key purpose OIDs

### Adding arbitrary extensions
# This requires to provide the extension OIDs, as well as the extension data in
# hex format. The following two options are available since GnuTLS 3.5.3.
#add_extension = "1.2.3.4 0x0AAB01ACFE"

# As above but encode the data as an octet string
#add_extension = "1.2.3.4 octet_string(0x0AAB01ACFE)"

# For portability critical extensions shouldn't be set to certificates.
#add_critical_extension = "5.6.7.8 0x1AAB01ACFE"

# When generating a certificate from a certificate
# request, then honor the extensions stored in the request
# and store them in the real certificate.
#honor_crq_extensions

# Alternatively only specific extensions can be copied.
#honor_crq_ext = 2.5.29.17
#honor_crq_ext = 2.5.29.15

# Path length contraint. Sets the maximum number of
# certificates that can be used to certify this certificate.
# (i.e. the certificate chain length)
#path_len = -1
#path_len = 2

# OCSP URI
# ocsp_uri = http://my.ocsp.server/ocsp

# CA issuers URI
# ca_issuers_uri = http://my.ca.issuer

# Certificate policies
#policy1 = 1.3.6.1.4.1.5484.1.10.99.1.0
#policy1_txt = "This is a long policy to summarize"
#policy1_url = http://www.example.com/a-policy-to-read

#policy2 = 1.3.6.1.4.1.5484.1.10.99.1.1
#policy2_txt = "This is a short policy"
#policy2_url = http://www.example.com/another-policy-to-read

# Name constraints

# DNS
#nc_permit_dns = example.com
#nc_exclude_dns = test.example.com

# EMAIL
#nc_permit_email = "nmav@ex.net"

# Exclude subdomains of example.com
#nc_exclude_email = .example.com

# Exclude all e-mail addresses of example.com
#nc_exclude_email = example.com

# IP
#nc_permit_ip = 192.168.0.0/16
#nc_exclude_ip = 192.168.5.0/24
#nc_permit_ip = fc0a:eef2:e7e7:a56e::/64

# Options for proxy certificates
#proxy_policy_language = 1.3.6.1.5.5.7.21.1

# Options for generating a CRL

# The number of days the next CRL update will be due.
# next CRL update will be in 43 days
#crl_next_update = 43

# this is the 5th CRL by this CA
# Comment the field for a time-based number.
#crl_number = 5

# Specify the update dates more precisely.
#crl_this_update_date = "2004-02-29 16:21:42"
#crl_next_update_date = "2025-02-29 16:24:41"

# The date that the certificates will be made seen as
# being revoked.
#crl_revocation_date = "2025-02-29 16:24:41"
\end{verbatim}

      \paragraph{Certificate Signing Request}
Creating of CSR is made by:
\begin{verbatim}
certtool --generate-request --load-privkey [keyfile.pem] \
         [--template cert.cfg]--outfile [csrfilename.pem]
\end{verbatim}

when not using template it uses default values 
%need to find out what those are
      \paragraph{Specify length}
Length is specified when generating keys by \verb+--sec-param=[low|legacy|medium|high|ultra]+ where length is determined by alias and algorithm.
For RSA:
\begin{verbatim}
low    = 1024 bit
legacy = 1776 bit
medium = 2048 bit
high   = 3072 bit
ultra  = 15424 bit
\end{verbatim}
For DSA:
\begin{verbatim}
low    = 1024 bit
legacy = 2048 bit
medium = 2048 bit
high   = 3072 bit
ultra  = 3072 bit
\end{verbatim}
For ECDSA:
\begin{verbatim}
low    = 160 bit
legacy = 192 bit
medium = 224 bit
high   = 256 bit
ultra  = 512 bit
\end{verbatim}

to define a hash algorithm use \verb+--hash=[SHA1|RMD160|SHA256|SHA384|SHA512+ option while generating a certificate.
      \paragraph{Specify algorithm}
Algorithm for key generation is specified in \verb+--[rsa|dsa|ecc]+ option where rsa = RSA, dsa = DSA, ecc = ECDSA.

@@

      \paragraph{Specify Type}
To specify whether certificate should be CA or End cert write \verb+ca+ into the cert.cfg file and use that as a template for generation. 
      \paragraph{Specify path length}
Path length is specified by \verb+path_len=<value>+ option in cert.cfg file, where value is max chain length ( use -1 for undefined value).

@@

    \subsubsection{Certificate Signing Request signing}
Possible %but i need to look wy it does not work for me
    \subsubsection{Create combination of private key and signed chain}
When you create a certificate by signing a request to sign key only, you can validate chain. %but i think that is not what is regarded here as signed chain    
    \subsubsection{Specify certificate validity}
Validity is specified by changing cert.cfg file used while generating a certificate, the part \verb+expiration_days = <value>+
Alternatively, you cen set NOT BEFORE and NOT AFTER times by changing \verb+activation_date = <NOT_BEFORE_STRING>+ and \verb+expiration_date = <NOT_AFTER_STRING>+ where the times are written in GNU date string format.

    \subsubsection{Setting Subject Alternative Name for end certificates}
SAN is set by adding options to cert.cfg :
\begin{verbatim}
dns_name = "www.dnsname1.com"
dns_name = "www.dnsname2.com"
  ...
dns_name = "www.lastdns.com"

uri = "uri1"
...

ip_address = "0.0.0.1"
ip_address = "0.0.0.2"
   ...
\end{verbatim}

    \subsubsection{Support for Cryptographic Service Provider}
GnuTLS does not have support for CSP.
\section{Conversions}

@@

    \subsubsection{Private key only}
It is not possible to export private key only, however for proper use of GnuTLS keys need to be stored on drive or imported to PKCS\#12 file.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
Not possible.
  \subsection{Importing certificates and keys into storage files}
Possible. - need to run up some facts.
